A GPU Sonar Simulator for Automatic Target Recognition

### 2014-05-12 Simulator/article.tex
la2pdf commit - 2014:05:09	12:00:25	(Fri 9.May)
la2pdf commit - 2014:05:09	12:46:36	(Fri 9.May)
la2pdf commit - 2014:05:12	13:12:15	(Mon12.May)
la2pdf commit - 2014:05:12	14:23:15	(Mon12.May)

%\usepackage{stfloats}                          % Allows: \begin{figure*}[!b]
                                                % (double column figures on top/bottom)

@@

\begin{figure}[t]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/simulator.svg}%
\caption{Simulator concept.}\label{buildup}%
\end{figure}

@@

The next step is to scale, orient and position the objects in the scene, and finally project this scene onto an image plane. This is achieved by applying a set of transformations to each vertex in the model. In OpenGL, the set of transformations is usually formalized like this:
\begin{align*}
\bmat{x\\y\\0\\1}_\text{image} = \P \cdot \V \cdot \M \cdot \bmat{x\\y\\z\\1}_\text{model},
\end{align*}
where $\bmat{\cdot}_\text{model}$ is the loaded model, $\bmat{\cdot}_\text{image}$ is the output image, and $\M$, $\V$ and $\P$ are transformation matrices. The first transform we apply is the model matrix $\M$, which scales and rotates the model in its local coordinate system. Then we map this model into world coordinates using the view matrix $\V$. This involves translating the model to its respectful place in the world, and then moving it into the view of the camera. Finally the relevant part of the scene is projected onto the image plane with a projection matrix $\P$.

\begin{align*}
\left(\begin{matrix}
x_c \\ y_c \\ z_c \\ w_c
\end{matrix}\right)
= \left(\begin{matrix}
\frac{2}{r-l}  &  0              &  0              &  -\frac{r+l}{r-l} \\
0              &  \frac{2}{t-b}  &  0              &  -\frac{t+b}{t-b} \\
0              &  0              &  \frac{-2}{f-n} &  -\frac{f+n}{f-n} \\
0              &  0              &  0              &  1
\end{matrix}\right)
\left(\begin{matrix}
x_e \\ y_e \\ z_e \\ w_e
\end{matrix}\right)
\end{align*}
where
\begin{align*}
l &=   &  r &= \\
b &=   &  t &= \\
f &=   &  n &= 
\end{align*}

@@

We place, resize and orient objects in an euclidean 3D space using suitable transformation matrices that are applied to each of the object's vertices:
\begin{align}
\bmat{x_t \\ y_t \\ z_t \\ w} &= \boldsymbol{T}\R\boldsymbol{S} \bmat{x \\ y \\ z \\ w}_\text{model}.
\end{align}
Here a model vertex at position $(x,y,z)$ is first scaled with $\boldsymbol{S}$, then rotated with $\R$
There is nothing special to these matrices, but we supply them here for completeness.

>>>>

\usepackage{stfloats}                          % Allows: \begin{figure*}[!b]
                                                % (double column figures on top/bottom)

@@

\begin{figure*}[t]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/simulator.svg}%
\caption{Simulator concept.}\label{buildup}%
\end{figure*}

@@

The next step is to scale, orient and position the objects in the scene, and finally project this scene onto an image plane. This is achieved by applying a set of transformations to each vertex in the model. In OpenGL, the set of transformations is usually formalized like this:
\begin{align*}
\bmat{x\\y\\0\\1}_\text{image} = \P \cdot \V \cdot \M \cdot \bmat{x\\y\\z\\1}_\text{model},
\end{align*}
where $\bmat{\cdot}_\text{model}$ is the loaded model, $\bmat{\cdot}_\text{image}$ is the output image, and $\M$, $\V$ and $\P$ are transformation matrices. The first transform we apply is the model matrix $\M$ which operates on the model's local coordinate system. It is defimed as
\begin{align}
\bmat{x_t \\ y_t \\ z_t \\ w}_\text{\parbox{1cm}{\setlength\baselineskip{0.3cm}transformed\\model}} &= \boldsymbol{T}\R\boldsymbol{S} \bmat{x \\ y \\ z \\ w}_\text{model}.
\end{align}
where $\boldsymbol{S}, \R and \boldsymbol{T}$ are matrices for scaling, rotation and translation, respectively. These are described in Appendix \ref{transformation_matrices}.

which scales and rotates the model in its local coordinate system. Then we map this model into world coordinates using the view matrix $\V$. This involves translating the model to its respectful place in the world, and then moving it into the view of the camera. Finally the relevant part of the scene is projected onto the image plane with a projection matrix $\P$.

\begin{align}
\P = \left(\begin{matrix}
\frac{2}{r-l}  &  0              &  0              &  -\frac{r+l}{r-l} \\
0              &  \frac{2}{t-b}  &  0              &  -\frac{t+b}{t-b} \\
0              &  0              &  \frac{-2}{f-n} &  -\frac{f+n}{f-n} \\
0              &  0              &  0              &  1
\end{matrix}\right)
\end{align}
where
\begin{align*}
l &= x_\text{min}  &  r &= x_\text{max}\\
b &=   &  t &= \\
f &=   &  n &= 
\end{align*}

@@

\section{Transformation matrices}\label{transformation_matrices} 
We place, resize and orient objects in an euclidean 3D space using suitable transformation matrices that are applied to each of the object's vertices:
\begin{align}
\bmat{x_t \\ y_t \\ z_t \\ w}_\text{\parbox{1cm}{\setlength\baselineskip{0.3cm}transformed\\model}} &= \boldsymbol{T}\R\boldsymbol{S} \bmat{x \\ y \\ z \\ w}_\text{model}.
\end{align}
Here a model vertex at position $(x,y,z)$ is first scaled with $\boldsymbol{S}$, then rotated with $\R$
There is nothing special to these matrices, but we supply them here for completeness.
